NAO robot that imitates human movements using Mediapipe\\

### 2024-02-14 Paper/main.tex
[write] new main.pdf not editable

\begin{abstract}
In this project, we programmed a NAO robot from Aldebaran to mimic human movements captured by a webcam using Mediapipe. While this type of human imitation has been done before, we aimed to approach it differently. Unlike most other projects utilizing multiple cameras or depth sensors like the LIDAR sensor, our focus was on a novel methodology.
The project is still in progress, with the robot currently capable of moving its arms, albeit not with high precision. Nonetheless, we see this as a promising starting point for future developments in computer vision and robotics.
\end{abstract}

\begin{IEEEkeywords}
NAO, Mediapipe, Human imitation, aldebaran, robotics
\end{IEEEkeywords}
% State of the art
\section{State of the art}
In this section, we will explore various methods for controlling the movement of a NAO robot using the Mediapipe Framework, as well as discuss related work involving human imitation with the NAO robot.

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.48\textwidth]{images/landmarksMP.jpeg}}
\caption{Landmarks from the Mediapipe library.}
\label{fig:landmarksMP}
\end{figure}

@@

\section{Approach}

\subsection{Objectives}

@@

\begin{figure}[htbp]
    \centerline{\includegraphics[width=0.5\textwidth]{images/RightArmAngles.jpeg}}
    \caption{Landmarks from the Mediapipe library.}
    \label{fig:RightArmAngles}
    \end{figure}

@@

We decided to use sockets to send the data, as we got inspiration from a project that we found with a similiar approach, in which the author used sockets to send the data from a kinect sensor to the robot.
This solved everything, about the connection between the scripts, because it uses the client-server approach, allowing me to use python 3.10 for the computer vision part that is the client and python 2.7 for the Robot movement part that is the server. We just had to do some encoding to send the data.

@@

Also the display of the images was very slow since the code had a delay to send the data, in order for the server to process it. We solved this using a thread to get the data from the displayed image and send it to the server with the thread without messing up with the display.
\\
As we said before after changing a lot the parameters and definition of the functions that were implemented before we realized that we was not sending the right data to the robot from the server, so we decided to change the approach and instead of sending the coordenates of the landmarks to the server, we decided to send the angles between them and send them directly to the server. This would help me to see what angles we was sending to the robot by showing them on the displayed image.

@@

% CONTRIBUCIONES
\section{Contribution}
% diferencias entre mi proyecto y los otros y como contribuye mi proyecto al estado del arte
The main difference between my project and the others is that it has a different approach to solve the problem, relying only on one camera and machine learning to detect and recreate the human poses, instead of using a lot of sensors. This is a contribution to the state of the art, because it implies that if there were better machine learning models, the robot could imitate the human movements in a better way. 
There is also a contribution to the work done before in "Mimetización de movimiento por robot antropomorfo basado en imágenes de sensor de profundidad" \cite{b3}, because we can see the angles that are being sent to the robot, which can be useful for further research.

@@

% Acknowledgment
\section*{Acknowledgment}
We want to thank my proffesor, Dr. Christian Groth for helping us during the project and thank also to the Hof University of Applied Science for giving us the opportunity to work with the NAO robot, which was a great experience.

>>>>

\begin{abstract}
In this project, we programmed a NAO robot from Aldebaran to mimic human movements captured by a webcam using Mediapipe. While this type of human imitation has been done before, we aimed to approach it differently. Unlike most other projects utilizing multiple cameras or depth sensors like the LIDAR sensor, our focus was on a novel methodology.
The project is still in progress, with the robot currently capable of moving its arms, albeit not with high precision. Nonetheless, we see this as a promising starting point for future developments in computer vision and robotics.
\end{abstract}
\begin{IEEEkeywords}
NAO, Mediapipe, Human imitation, aldebaran, robotics
\end{IEEEkeywords}
% State of the art
\section{State of the art}
In this section, we will explore various methods for controlling the movement of a NAO robot using the Mediapipe Framework, as well as discuss related work involving human imitation with the NAO robot.

@@

\begin{figure}[htbp]
    \label{fig:landmarksMP}
    \centerline{\includegraphics[width=0.48\textwidth]{images/landmarksMP.jpeg}}
    \caption{Landmarks from the Mediapipe library.}
\end{figure}

@@

\section{Approach}
\subsection{Objectives}

@@

\begin{figure}[htbp]
    \label{fig:RightArmAngles}
    \centerline{\includegraphics[width=0.5\textwidth]{images/RightArmAngles.jpeg}}
    \caption{Joints in the arm of the NAO robot.}
\end{figure}

@@

We decided to use sockets to send the data, as we got inspiration from a project that we found with a similiar approach, in which the author used sockets to send the data from a kinect sensor to the robot.
This solved everything, about the connection between the scripts, because it uses the client-server approach, allowing us to use python 3.10 for the computer vision part that is the client and python 2.7 for the Robot movement part that is the server. We just had to do some encoding to send the data.

@@

Also the display of the images was very slow since the code had a delay to send the data, in order for the server to process it. We solved this using a thread to get the data from the displayed image and send it to the server with the thread without messing up with the display.
\\
As we said before after changing a lot the parameters and definition of the functions that were implemented before we realized that we was not sending the right data to the robot from the server, so we decided to change the approach and instead of sending the coordenates of the landmarks to the server, we decided to send the angles between them and send them directly to the server. This would help us to see what angles we was sending to the robot by showing them on the displayed image.

@@

% CONTRIBUCIONES
\section{Contribution}
% diferencias entre mi proyecto y los otros y como contribuye mi proyecto al estado del arte
The main difference between our project and the others is that it has a different approach to solve the problem, relying only on one camera and machine learning to detect and recreate the human poses, instead of using a lot of sensors. This is a contribution to the state of the art, because it implies that if there were better machine learning models, the robot could imitate the human movements in a better way. 
There is also a contribution to the work done before in "Mimetización de movimiento por robot antropomorfo basado en imágenes de sensor de profundidad" \cite{b3}, because we can see the angles that are being sent to the robot, which can be useful for further research.

@@

% Acknowledgment
\section*{Acknowledgment}
We want to thank our proffesor, Dr. Christian Groth for helping us during the project and thank also to the Hof University of Applied Science for giving us the opportunity to work with the NAO robot, which was a great experience.
